---
title: "Assignement1"
author: "Zain Mudassar"
date: "2/18/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r Q1}
library(igraph)

```
 
## Data Loading 


```{r Q1(A)}
Political<- read.graph("polblogs.gml",format=c("gml"))
Neuralnet<- read.graph("celegansneural.gml",format=c("gml"))
Internet<- read.graph("as-22july06.gml",format=c("gml"))
books<-read.graph("polbooks.gml",format=c("gml"))
```

# Erdos-Renyi random networks G(n; p) using igraph.

```{r Q1(B)}
first <- erdos.renyi.game(2000, 0.01)
second <- erdos.renyi.game(2000, 0.005)
third <- erdos.renyi.game(2000, 0.0025)

```

# Internet:


```{r Q1(C)}

Is_Directed <- is_directed(Internet)
print("Is directed or not")
Is_Directed

No_Nodes <- gorder(Internet)
print("Number of Nodes")
No_Nodes

No_Edges<-gsize(Internet)
print("Number of Edges ")
No_Edges

No_Connect_Components=groups(components(Internet,mode = c("weak", "strong")))
print("Number of connected components")

Max_Degree <-max(degree(Internet))
print("Maximum Degree ")
Max_Degree

```
```{r Q1(D)}

Avg_P_Length<-average.path.length(Internet)
print("Average Path Length")
Avg_P_Length

Diameter<-diameter(Internet)
print("Diameter")

Diameter


Avg_L_Cluster_Coefficient<-transitivity(Internet, type = c("localaverageundirected"))
print("Average Local Clustering Coefficient")

Avg_L_Cluster_Coefficient


Avg_G_Cluster_Coefficient<-transitivity(Internet, type = c("global"))
print("Average global clustering coefficient")

Avg_G_Cluster_Coefficient


plot(degree.distribution(Internet),xlab="Pk", ylab="k")

plot(path.length.hist(Internet)$res,xlab="Pl", ylab="l")


```



# Political

```{r Q2(A)}
Is_Directed <- is_directed(Political)
print("Is directed or not")
Is_Directed

No_Nodes <- gorder(Political)
print("Number of Nodes")
No_Nodes

No_Edges<-gsize(Political)
print("Number of Edges ")
No_Edges

No_Connect_Components=groups(components(Political,mode = c("weak", "strong")))
print("Number of connected components")

Max_Degree <-max(degree(Political))
print("Maximum Degree ")
Max_Degree

```

```{r Q2(B)}
Avg_P_Length<-average.path.length(Political)
print("Average Path Length")
Avg_P_Length

Diameter<-diameter(Political)
print("Diameter")

Diameter


Avg_L_Cluster_Coefficient<-transitivity(Political, type = c("localaverageundirected"))
print("Average Local Clustering Coefficient")

Avg_L_Cluster_Coefficient


Avg_G_Cluster_Coefficient<-transitivity(Political, type = c("global"))
print("Average global clustering coefficient")

Avg_G_Cluster_Coefficient


plot(degree.distribution(Political),xlab="Pk", ylab="k")

plot(path.length.hist(Political)$res,xlab="Pl", ylab="l")


```


# Neural Network:

```{r Q3(A)}
Is_Directed <- is_directed(Neuralnet)
print("Is directed or not")
Is_Directed

No_Nodes <- gorder(Neuralnet)
print("Number of Nodes")
No_Nodes

No_Edges<-gsize(Neuralnet)
print("Number of Edges ")
No_Edges

No_Connect_Components=groups(components(Neuralnet,mode = c("weak", "strong")))
print("Number of connected components")
No_Connect_Components

Max_Degree <-max(degree(Neuralnet))
print("Maximum Degree ")
Max_Degree

```


```{r Q3(B)}
Avg_P_Length<-average.path.length(Neuralnet)
print("Average Path Length")
Avg_P_Length

Diameter<-diameter(Neuralnet)
print("Diameter")

Diameter


Avg_L_Cluster_Coefficient<-transitivity(Neuralnet, type = c("localaverageundirected"))
print("Average Local Clustering Coefficient")

Avg_L_Cluster_Coefficient


Avg_G_Cluster_Coefficient<-transitivity(Neuralnet, type = c("global"))
print("Average global clustering coefficient")
Avg_G_Cluster_Coefficient


plot(degree.distribution(Neuralnet),xlab="Pk", ylab="k")

plot(path.length.hist(Neuralnet)$res,xlab="Pl", ylab="l")
```



# Erdos-Renyi random networks (parameters n = 2000 and p = 0:01);

```{r Q4(A)}
Is_Directed <- is_directed(first)
print("Is directed or not")
Is_Directed

No_Nodes <- gorder(first)
print("Number of Nodes")
No_Nodes

No_Edges<-gsize(first)
print("Number of Edges ")
No_Edges

No_Connect_Components=groups(components(first,mode = c("weak", "strong")))
print("Number of connected components")

Max_Degree <-max(degree(first))
print("Maximum Degree ")
Max_Degree

```


```{r Q4(B)}
Avg_P_Length<-average.path.length(first)
print("Average Path Length")
Avg_P_Length

Diameter<-diameter(first)
print("Diameter")

Diameter


Avg_L_Cluster_Coefficient<-transitivity(first, type = c("localaverageundirected"))
print("Average Local Clustering Coefficient")

Avg_L_Cluster_Coefficient


Avg_G_Cluster_Coefficient<-transitivity(first, type = c("global"))
print("Average global clustering coefficient")
Avg_G_Cluster_Coefficient


plot(degree.distribution(first),xlab="Pk", ylab="k")

plot(path.length.hist(first)$res,xlab="Pl", ylab="l")
```




# Erdos-Renyi random networks (parameters n = 2000 and p = 0:005);

```{r Q5(A)}
Is_Directed <- is_directed(second)
print("Is directed or not")
Is_Directed

No_Nodes <- gorder(second)
print("Number of Nodes")
No_Nodes

No_Edges<-gsize(second)
print("Number of Edges ")
No_Edges

No_Connect_Components=groups(components(second,mode = c("weak", "strong")))
print("Number of connected components")


Max_Degree <-max(degree(second))
print("Maximum Degree ")
Max_Degree

```


```{r Q5(B)}
Avg_P_Length<-average.path.length(second)
print("Average Path Length")
Avg_P_Length

Diameter<-diameter(second)
print("Diameter")

Diameter


Avg_L_Cluster_Coefficient<-transitivity(second, type = c("localaverageundirected"))
print("Average Local Clustering Coefficient")

Avg_L_Cluster_Coefficient


Avg_G_Cluster_Coefficient<-transitivity(second, type = c("global"))
print("Average global clustering coefficient")
Avg_G_Cluster_Coefficient


plot(degree.distribution(second),xlab="Pk", ylab="k")

plot(path.length.hist(second)$res,xlab="Pl", ylab="l")
```



# Erdos-Renyi random networks (parameters n = 2000 and p = 0:0025);

```{r Q6(A)}
Is_Directed <- is_directed(third)
print("Is directed or not")
Is_Directed

No_Nodes <- gorder(third)
print("Number of Nodes")
No_Nodes

No_Edges<-gsize(third)
print("Number of Edges ")
No_Edges

No_Connect_Components=groups(components(third,mode = c("weak", "strong")))
print("Number of connected components")

Max_Degree <-max(degree(third))
print("Maximum Degree ")
Max_Degree

```


```{r Q6(B)}
Avg_P_Length<-average.path.length(third)
print("Average Path Length")
Avg_P_Length

Diameter<-diameter(third)
print("Diameter")

Diameter


Avg_L_Cluster_Coefficient<-transitivity(third, type = c("localaverageundirected"))
print("Average Local Clustering Coefficient")

Avg_L_Cluster_Coefficient


Avg_G_Cluster_Coefficient<-transitivity(third, type = c("global"))
print("Average global clustering coefficient")
Avg_G_Cluster_Coefficient


plot(degree.distribution(third),xlab="Pk", ylab="k")

plot(path.length.hist(third)$res,xlab="Pl", ylab="l")
```

# Analysis of "Books of US politics":
# Description: 
I have worked on "Books of US politics" dataset. The nodes in the data represent the books about US politics sold by Amazon.com.Edges are representing frequently co-purchased books by the same buyers, as indicated by the "customers who bought this book also bought these other books" feature on Amazon. There are three values given to nodes which are "l" "n" "c", which stands for "liberal", "neutral", or "conservative". 


```{r Q7(A)}
Is_Directed <- is_directed(books)
print("Is directed or not")
Is_Directed

No_Nodes <- gorder(books)
print("Number of Nodes")
No_Nodes

No_Edges<-gsize(books)
print("Number of Edges ")
No_Edges

No_Connect_Components=groups(components(books,mode = c("weak", "strong")))
print("Number of connected components")

Max_Degree <-max(degree(books))
print("Maximum Degree ")
Max_Degree

```


```{r Q7(B)}
Avg_P_Length<-average.path.length(books)
print("Average Path Length")
Avg_P_Length

Diameter<-diameter(books)
print("Diameter")

Diameter


Avg_L_Cluster_Coefficient<-transitivity(books, type = c("localaverageundirected"))
print("Average Local Clustering Coefficient")

Avg_L_Cluster_Coefficient


Avg_G_Cluster_Coefficient<-transitivity(books, type = c("global"))
print("Average global clustering coefficient")
Avg_G_Cluster_Coefficient


plot(degree.distribution(books),xlab="Pk", ylab="k")

plot(path.length.hist(books)$res,xlab="Pl", ylab="l")
```



